A Multi-Modal Model for Prediction and Classification of Object Deformation during Robotic Manipulation

### 2016-04-14 twostagedo.tex
added some more text to link to journal theme

As has been mentioned above there are several choices made in our modelling approach. The key choice is that the models are generative, which means that the models can be used to generate predicted sequences of behaviour. The specific approach taken here separates the predictive model out into components in two ways (see Figure~\ref{fig:system}). First we decompose models according to the modality of the information. In this case it is important to note that deformation has a particular causal structure related to the modes of sensing that are most easily employed. The forces and deformations can be measured separately, using force-torque and visual sensors respectively. The sensed forces are the cause of the observed deformation, and this can be exploited by sequencing the models by mode. Thus the input to the first predictor is the planned motion of the robot (or the joint torques), and this predictor predicts the resulting sequence of contact forces. The second predictor takes this sequence of forces as input and predicts a deformation sequence. Both models must be conditioned on the material and the object. This is where we decompose the model space in the second way, by specialising models to particular material and object combinations. This follows the principle of modular motor learning \cite{KopickiICRA11,haruno2001mosaic}, where prediction and control is specialised into many modules, each of which covers a relatively small portion of the input space, such as an object or material type. Thus we aim to acquire many specialist models of different deformable objects rather than a very few rather general models. The specific model forms we choose here could be replaced while retaining the overall scheme. In this paper we implement the scheme using a regression approach to force prediction, and we follow several other authors in employing a mass-spring system with learnable parameters for the deformation prediction.

@@

\section{Discussion}
\label{sec:discussion}
We note the following points about the results and the method in general.
\subsection{The Learning Method}
Even though the evolutionary algorithm allowed for a uniform exploration of the logarithmic space of parameters, it failed to improve the quality of the simulations as much as it could.  Better simulations have been obtained by hand tunning some of the parameters.  \sout{A factor that this learning algorithm fails to take into account are the significant differences in behaviour when the magnitude of a parameter is modified in factors of 10.  The random uniform distribution used to select parameters favors a given order of magnitude while the system would benefit more from stronger variantions here.}

@@

\subsection{Conclusions}
In summary we have presented a framework, together with specific algorithms for learning the deformable behaviour of objects from robotic interaction. The main properties of the model are as follows. First, the parameters for the model were adjusted to data from real objects under robotic interaction. Second, we have attempted the automatic callibration of a simulation of plasticity. Third we use regression to predict the reaction forces. Fourth we include a new energy term for the preservation of angles of the mesh's triangles. Fifth we employ a regularization algorithm for a linear snake, that increases or decreases the number of its control points, according to the level of detail required to represent the deformed object. Sixth we provide a detailed evaluation of the dynamic simulation, instead of only during its stable states as in previous work. Finally we showed the application of the model to the problem of classifying deformable materials.

@@

The authors would like to thank Rustam Stolkin for his help in setting up the data gathering experiments and for the construction of the robotic finger. The research leading to this results has received funding from the PhD Scholarships program of CONACYT, Mexico and from the European Community's Seventh Framework Program [FP7/2007-2013] under grant agreements 215181 CogX, and 600918 PaCMan.

>>>>

As has been mentioned above there are several choices made in our modelling approach. The key choice is that the models are generative, which means that the models can be used to generate predicted sequences of behaviour. The specific approach taken here separates the predictive model out into components in two ways (see Figure~\ref{fig:system}). First we decompose models according to the modality of the information. In this case it is important to note that deformation has a particular causal structure related to the modes of sensing that are most easily employed. The forces and deformations can be measured separately, using force-torque and visual sensors respectively. The sensed forces are the cause of the observed deformation, and this can be exploited by sequencing the models by mode. Thus our approach can be seen as a sensorimotor contingency in which two contigencies are sequenced to produce an overall prediction. The input to the first predictor is the planned motion of the robot (or the joint torques), and this predictor predicts the resulting sequence of contact forces. The second predictor takes this sequence of forces as input and predicts a deformation sequence. Both models must be conditioned on the material and the object. This is where we decompose the model space in the second way, by specialising models to particular material and object combinations. This follows the principle of modular motor learning \cite{KopickiICRA11,haruno2001mosaic}, where prediction and control is specialised into many modules, each of which covers a relatively small portion of the input space, such as an object or material type. Thus we aim to acquire many specialist models of different deformable objects rather than a very few rather general models. The specific model forms we choose here could be replaced while retaining the overall scheme. In this paper we implement the scheme using a regression approach to force prediction, and we follow several other authors in employing a mass-spring system with learnable parameters for the deformation prediction.

@@

\section{Discussion}
\label{sec:discussion}
We note the following points about the results and the method in general.
\subsection{The Learning Method}
Even though the evolutionary algorithm allowed for a uniform exploration of the logarithmic space of parameters, it failed to improve the quality of the simulations as much as it could.  Better simulations have been obtained by hand tunning some of the parameters.  %\sout{A factor that this learning algorithm fails to take into account are the significant differences in behaviour when the magnitude of a parameter is modified in factors of 10.  The random uniform distribution used to select parameters favors a given order of magnitude while the system would benefit more from stronger variantions here.}

@@

\subsection{Conclusions}
In summary we have presented a framework, together with specific algorithms for learning the sensorimotor contingencies for the deformable behaviour of objects under robot manipulation. We have developed a learning model that learns the parameters of two contingencies that are sequenced, one for kinematic motion to force and the other for force to deformation. By sequencing these we obtained a compound contingency that predicts deformation given motion. The main properties of the model are as follows. First, the parameters for the model were adjusted to data from real objects under robotic manipulation. Second, we have attempted the automatic calibration of a simulation of plasticity. Third we use regression to predict the reaction forces. Fourth we include a new energy term for the preservation of angles of the mesh's triangles. Fifth we employ a regularization algorithm for a linear snake, that increases or decreases the number of its control points, according to the level of detail required to represent the deformed object. Sixth we provide a detailed evaluation of the dynamic simulation, instead of only during its stable states as in previous work. Finally we showed the application of the model to the problem of classifying deformable materials.

@@

We gratefully acknowledge funding from the PhD Scholarship program of CONACYT, Mexico and from the European Community's FP7 program, under grant agreements 215181 CogX, and 600918 PaCMan.
